MSE and dynamic state variable model with sigma function

### 2018-05-15 doc/previous versions/MSE_JAN_18.tex
splitted code and plots

Once the backward calculations were finished, the forward part is a Monte Carlo simulation where the probabilities of choices were sampled randomly using the probabilities in ~\ref{eq:solve}. This was done for 700 individual vessels.

\begin{table}[!h]
\centering
\caption{Model and fishery conditioning.}
\label{t:fishery}
\resizebox{0.9\textwidth}{!}{%
\begin{tabular}{@{}lc lc lc @{}} 
\hline
\textbf{model}                              &               & \textbf{Fishery variable costs}                &      &\textbf{Fishery }&  \\ \hline
& & & \\%& & \\
number of vessels                           &700            &fuel costs (Euro day\textsuperscript{-1})       & 150  & q                 & 0.0005 \\ 
$\sigma $                                   & 40            &gear maintenance (Euro day\textsuperscript{-1}) & 0    & effort (p,s)      & 1   \\
number of areas                             & 2             &crew share                                      & 35\% & CPUE & mean($pop*q*wts(yy-2:yy)$)\\
number of seasons                           & 6             &landing costs (Euro t\textsuperscript{-1})      & 0    & CPUE dev& $0.08*CPUE$\\
intial quota $Q_{sp1}$ and $Q_{sp2}$  & 200&                 &      \\%& & \\
& & & \\\hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependant pricing}
\label{sec2.2.1}
Prices of fish have been assumed to be fixed over time but influenced by the size of the catch. Common knowledge and case studies indicate that size and weight of a fish could be important attributes when determining its economic value \cite{Zimmermann2011, Zimmermann2013}. Therefore, the resulting data of mean weights and average prices were used for further analysis. We fitted linear mixed models, using mean price and mean body weight as the response variable and covariate, respectively. Thus, following \cite{Zimmermann2011}, the statistical models took the form:  
\begin{equation}
 pw_{i} \sim p_i \bar{w_i} + \beta_0 \times \frac{w_i-\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p$ is the mean price of species $i$, $\bar{w_i}$ is the mean weight of the corresponding weight classes, and the fraction corresponded to the standarization of the mass relative to the mean observed individual catch mass over all ages classes. $\beta_0$ gave the price increase when individial mass was increased by $\bar{w}$. We used mean prices of 150 Euro kg\textsuperscript{-1} for both species.
 %Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Linear mass-prices estimated based on mean prices per mass age-classes. The price slopes $\beta_0$ were assumed to be similar to mean prices.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}lcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
                         & 1     & 2     & 3    & 4   \\ \hline
                      \\
species 1                &  778  & 1354   & 1780  & 2096  \\
species 2                &  778  & 1354   & 1780  & 2096  \\
\\
\hline 
\end{tabular}
}
\end{table}

@@

The three management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These manegemet strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l c c  c }
\hline
                                & \textbf{Scenario I}            & \textbf{Scenario II}                 & \textbf{Scenario III}           \\ 
                                & \textit{(landings selectivity)}& \textit{(fulll avoidance of discards)} & \textit{(LO not fully enforced)} \\ \hline
& & &  \\
Discarding                      & Allowed                        & Not allowed                          & Ocurred but not perceived \\
Manager catch perception        & $C = L + D$                    &        $C = L$ ($D = 0$)                      &  $C = L$ ($D \neq 0$) \\
Selectivity ($l_{ratio}$)         &  $ \neq 1$                     & $=1$                                 & $=1$\\
Yield per recruitment model     & based in $F_L$                 &       based in $F_C$                 &  based in $F_L$  \\

&  & &  \\\hline
\end{tabular}
}
\end{table}

@@

\newpage
%\begin{landscape}
Scenario I:
%----------------------------------------------------------------------------------------------------------------------------------------
\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_LO_disc_YieldLand1.eps} 
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_LO_disc_YieldLand1.eps} 
\end{minipage}
\caption{}
\end{figure}
%\end{landscape}

@@

Scenario II:
%----------------------------------------------------------------------------------------------------------------------------------------
\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_LO.eps} 
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_LO.eps} 
\end{minipage}
\caption{}
\end{figure}

Scenario III:

\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_LO_nocompliance.eps}  
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\centering
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_LO_nocompliance.eps} 
\end{minipage}
\caption{}
\label{fig:effort_lo}
\end{figure}

\subsection{Simulated catch decisions and location choice}
\label{sec3.1}

>>>>

Once the backward calculations were finished, the forward part is a Monte Carlo simulation where the probabilities of choices were sampled randomly using the probabilities in~\ref{eq:solve}. This was done for 700 individual vessels.

\begin{table}[!h]
\centering
\caption{Model and fishery conditioning.}
\label{t:fishery}
\resizebox{0.9\textwidth}{!}{%
\begin{tabular}{@{}lc lc lc @{}} 
\hline
\textbf{model}                              &               & \textbf{Fishery variable costs}                &      &\textbf{Fishery }&  \\ \hline
& & & \\%& & \\
number of vessels                           &700            &fuel costs (Euro day\textsuperscript{-1})       & 1240  & q                 & 0.0005 \\ 
$\sigma $                                   & 40            &gear maintenance (Euro day\textsuperscript{-1}) & 0    & effort (p,s)      & 1   \\
number of areas                             & 2             &crew share                                      & 35\% & CPUE & mean($pop*q*wts(yy-2:yy)$)\\
number of seasons                           & 6             &landing costs (Euro t\textsuperscript{-1})      & 0    & CPUE dev& $0.08*CPUE$\\
intial quota $Q_{sp1}$ and $Q_{sp2}$  & 200&                 &      \\%& & \\
& & & \\\hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependent pricing}
\label{sec2.2.1}
Prices of fish have been assumed to be fixed over time but influenced by the size of the catch. Common knowledge and case studies indicate that size and weight of a fish could be important attributes when determining its economic value \cite{Zimmermann2011, Zimmermann2013}. Therefore, the resulting data of mean weights and average prices were used for further analysis. We fitted linear mixed models, using mean price and mean body weight as the response variable and covariate, respectively. Thus, following \cite{Zimmermann2011}, the statistical models took the form:  
\begin{equation}
 pw_{i} \sim p_i \bar{w_i} + \beta_0 \times \frac{w_i-\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p$ is the mean price of species $i$, $\bar{w_i}$ is the mean weight of the corresponding weight classes, and the fraction corresponded to the standarization of the mass relative to the mean observed individual catch mass over all ages classes. $\beta_0$ gave the price increase when individial mass was increased by $\bar{w}$. We used mean prices of 150 Euro kg\textsuperscript{-1} for both species.
 %Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Linear mass-prices estimated based on mean prices per mass age-classes. The price slopes $\beta_0$ were assumed to be similar to mean prices.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}llcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
&                         & 1     & 2     & 3    & 4   \\ \hline
                      \\
Scenario I &              &       &        &       &     \\                       
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  778  & 1354   & 1780  & 2096  \\
                      \\
Scenario II &              &       &        &       &     \\ 
&species 1                &  778  & 1354   & 1780  & 2096  \\
&species 2                &  778  & 1354   & 1780  & 2096  \\
\\
\hline 
\end{tabular}
}
\end{table}

@@

The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These manegemet strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\resizebox{0.8\textwidth}{!}{%
\begin{tabular}{l c c}
\hline
                                & \textbf{Scenario I}            & \textbf{Scenario II}                  \\ 
                                & \textit{(landings selectivity)}& \textit{(fulll avoidance of discards)}\\ \hline
& &   \\
Discarding                      & Allowed                        & Not allowed                 \\
Manager catch perception        & $C = L + D$                    &        $C = L$ ($D = 0$)    \\
Selectivity ($l_{ratio}$)       &  $ \neq 1$                     & $=1$                      \\
Yield per recruitment model     & based in $F_L$                 &       based in $F_C$          \\

&  &   \\\hline
\end{tabular}
}
\end{table}

@@

\newpage
%\begin{landscape}
Scenario I:
%----------------------------------------------------------------------------------------------------------------------------------------
\begin{figure}[!h]
\centering
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_scenarioI.eps} 
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_scenarioI.eps} 
\end{minipage}
\caption{}
\end{figure}
%\end{landscape}

@@

Scenario II:
%----------------------------------------------------------------------------------------------------------------------------------------
%\begin{figure}[!h]
%\centering
%\begin{minipage}{.45\textwidth}
%\includegraphics[width=0.9\textheight, angle=90]{Figures/Catch_scenarioII.eps} 
%\end{minipage}
%\hfill
%\begin{minipage}{.45\textwidth}
%\includegraphics[width=0.9\textheight, angle=90]{Figures/Effort_scenarioII.eps} 
%\end{minipage}
%\caption{}
%\end{figure}

\subsection{Simulated catch decisions and location choice}
\label{sec3.1}
When discarding was allowed, but TACs changed by 15\% based on previous year but trying approximate to Fmsy, TACS showed a reduction and discards increased.

The implementation of LO caused an increase in TACs and revenues were higher than when discarding was allowed.
